MINOS Handover Plots

### 2024-02-02 minos/validation/handovers.Rmd

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

#

#out.path <- here::here('output', 'scotland_scaled/')
#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)

# HR 283-285 older version (285)
# out.path <- here::here('output', 'child_poverty_config/')
# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
```

@@

@@

## CHILD POVERTY VARS

### Relative poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')

tit <- 'Relative Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'relative_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Absolute Poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')

tit <- 'Absolute Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'absolute_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Persistent Poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')

tit <- 'Persistent Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'persistent_poverty.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)

@@

### Low Income and Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')

tit <- 'Material Deprivation Child'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'low_income_matdep_child.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)

>>>>

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

## Hourly Wage

```{r}
handover_boxplots(raw.dat, base.dat, 'hourly_wage')
handover_lineplots(raw.dat, base.dat, 'hourly_wage')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, hourly_wage)
base.s <- base.dat %>%
  select(pidp, age, time, hourly_wage)

spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

# now a version limited to 0-100
spag <- spag %>%
  filter(hourly_wage <= 300)
spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

```{r}
# some basic statistics about hourly_wage variable
print("Some basic statistics on hourly_wage. These are all for 2020.")
raw.2020 <- raw.dat %>% filter(time == 2020)
print('All living people in 2020')
print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
# number individuals with an hourly_wage > 0
print('People not in work')
print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))

# Number in work
print('People in work')
print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))

# Extreme hourly_wage values
print('Extreme hourly wage values: HIGH')
print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))

raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
print('Extreme hourly wage values: LOW (non-zero)')
print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
```

## S7 Labour State

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')

lab.state <- prepped.list$var
lab.state.norm <- prepped.list$norm

# Now plot
ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_labour_state.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, lab.state, lab.state.norm)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_labour_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

```{r}

@@
